---
title: "Fitting Models"
author: 'Yawen Yu and Dan Yurovsky'
date: '`r Sys.Date()`'
output:
  pdf_document: default
  html_document: null
  toc: no
number_sections: no
theme: lumen
code_folding: hide
toc_float: no
---


```{r, global chunck options, include=FALSE}
knitr::opts_chunk$set(message=FALSE, results='markup',warning =  FALSE)
options(xtable.comment=FALSE)
```
```{r, setup, echo=FALSE, warning=FALSE}
library(mice)
library(tidyverse)
library(lme4)
load("~/Desktop/application/lexical diversity/trial_3_pre/CHILDES_Lexical-diversity.RData")
```


```{r}
## combine data of moms and their children, 134 in total
mom_id <- unique(mom_month_mtld$target_child_id)
combine_month_mtld <- child_month_mtld %>%
  filter(speaker_id %in% mom_id) 

combine_month_mtld <- child_month_mtld %>%
                      filter(speaker_id %in% mom_id) %>%
                      left_join(x=mom_month_mtld[, c("speaker_id", "age", "length", "mtld")],
                                by = c("speaker_id", "age"))


# linear regression
# children's LD versus mothers' LD
lm_child_mom <- lm(mtld.x ~ mtld.y, combine_month_mtld)
summary(lm_child_mom)

# add another variable log(age)
lm_child_mom_lg <-lm(mtld.x ~ mtld.y + log(age),combine_month_mtld)
summary(lm_child_mom_lg)
plot(fitted(lm_child_mom_lg), residuals(lm_child_mom_lg))


# Correlation is always significant in a large dataset 
# only look at moms' and children's LD at 24 months (69 kids)
combine_child_mom_24 <- combine_month_mtld[which(combine_month_mtld$age == 24),]
lm_child_mom_24 <- lm(mtld.x ~ mtld.y, combine_child_mom_24)
summary(lm_child_mom_24)
plot(fitted(lm_child_mom_24), residuals(lm_child_mom_24))

# moms' and children's LD at 30 months (65 kids)
combine_child_mom_30 <- combine_month_mtld[which(combine_month_mtld$age == 30),]
lm_child_mom_30 <- lm(mtld.x ~ mtld.y, combine_child_mom_30)
summary(lm_child_mom_30)
plot(fitted(lm_child_mom_30), residuals(lm_child_mom_30))

ggplot(combine_month_mtld,aes(mtld.y,mtld.x,color = speaker_id))+
  geom_point()+
  geom_smooth(method = "gam")+
  theme_classic()

# Results: All of models above show significant correlation between moms' LD and children's LD
# Next step: To examnine this correlation by controlling for age variable
```

* Granger Causality model 
```{r,message=F}
# 1) filter kids with observations during 20~35 months 
# 2) drop kids with more than 20% missing values 
filter_id <- function(df){
freq_age <- aggregate(df$mtld.x, by = list(age = df$age), length) 
df <- df[which(df$age > 19 & df$age < 36),]
df <- df[,c("speaker_id","age","mtld.x")]
number <- aggregate(df$mtld.x, by = list(speaker_id = df$speaker_id), length)
id <- number$speaker_id[which(number$x > (0.8 *16))]
df <- df %>%
  filter(speaker_id %in% id)
}

# get 14 kids in total
filter_child <- filter_id(combine_month_mtld)
id <- unique(filter_child$speaker_id) 

# 3)impute missing data
wide_data <- function(df){
df <- reshape(df , idvar = "age" , timevar = "speaker_id", direction = "wide")
df <- df[order(df$age),]
colnames(df) <- c("age",id)
df
}

filter_child_wide <- wide_data(filter_child)
```
```{r,results = 'hide'}
set.seed(500)
md.pattern(filter_child_wide)
impute_data <- mice(filter_child_wide,m=5,maxit=5,meth='pmm',seed=500)
summary(impute_data)
impute_data <- mice::complete(impute_data,1)

# convert to long format
long_data <- function(df){
age <- df$age
df <- gather(df, age, value, colnames(df[,2:15]), factor_key = TRUE)
colnames(df) <- c("age","speaker_id","mtld")
df
}

filter_child_impute <- long_data(filter_child_wide)

# combine imputed child data with moms
filter_combine <- merge(x = filter_child_impute,
  y = combine_month_mtld[, c("speaker_id", "age", "mtld.y")],
  by = c("speaker_id", "age"))
```
```{r,message=FALSE}
# 4) use Dickey-Fuller Test to check stationarity
tseries::adf.test(filter_combine$mtld, alternative = "stationary", k=0) # p-value < 0.05 indicates it is stationary

# 5) examine with Granger Casuality Model
# H0: development of kids' LD is independent of change of moms' LD
# Ha: development of kids' LD is dependent on change of moms' LD
kid_lag <- diff(filter_combine$mtld)
mom_mtld <- diff(filter_combine$mtld.y)
# we do not get enough evidence to reject the null hypothesis
lmtest::grangertest(kid_lag~mom_mtld, order = 2)
```


* Mixed-effect model I: cocurrent correlation between moms and children 
```{r,message=F}
lmer_child_mom_lg <-
  lmer(scale(mtld.x) ~ scale(mtld.y) -1  + log(age) + 
         (1 + log(age) | speaker_id),
          combine_month_mtld) # scale the MTLD values since kids normally have slighly lower LD

summary(lmer_child_mom_lg)

ggplot(fortify(lmer_child_mom_lg),aes(mtld.y, mtld.x, 
                                 color = speaker_id)) +
       stat_summary(aes(y = .fitted), fun.y = mean, geom = "line")

```

* Fixed effect model I: whether moms with low/moderate/high LD yield different influences 
```{r,message=F}
# group moms according to LD levels (low/moderate/high)
mu_mom <- mean(combine_month_dev$mtld.y,na.rm=TRUE)
sd_mom <- sd(combine_month_dev$mtld.y, na.rm=TRUE)
low <- mu_mom -  0.5 * sd_mom
high <- mu_mom +  0.5 * sd_mom

ggplot(combine_month_mtld,aes(mtld.y))+
  geom_histogram(bins = 30)+
  geom_vline(xintercept = low, color = "gold",size = 2)+
  geom_vline(xintercept = high, color = "gold",size = 2)

mom_dif = cut(combine_month_dev$mtld.y,
  breaks = c(14, low, high, 125),
  label = c("low", "moderate", "high"))

# high level moms better correlated with kids' development
lm_mom_dif <-lm(mtld.x ~  mom_dif , combine_month_dev)
summary(lm_mom_dif)

```


* Mixed effect model II: whether moms with low/moderate/high LD yield different influences 
```{r,message=F}
lmer_mom_dif <-lmer((mtld.x - lag.x) ~  mom_dif + (1 | speaker_id), combine_month_dev)
summary(lmer_mom_dif)

# add age variable
lmer_dif_age <- lmer((mtld.x - lag.x) ~   mom_dif + log(age) + 
                       (1 | speaker_id), combine_month_dev)
summary(lmer_dif_age)
```


* Fixed effect model II: Simple ARMA model 
```{r,results= 'hide'}
# get intercepts and slops for individual child
lm_dev <- lm(mtld.x ~ lag.x + (1+lag.x) * factor(speaker_id) , data = combine_month_dev)
summary(lm_dev)
```


* Mixed-effect model III: whether different moms extert different influences on the DEVELOPMENT of kids' LD 
```{r,message=F}
# filter kids with more than 2 observations
mtld_filter <- function(df) {
  nmtld <- aggregate(child_data_mtld$mtld,
  by = list(speaker_id = child_data_mtld$speaker_id),
  length)
  nchild <- nmtld$speaker_id[(nmtld$x > 5)]
  df <- df %>%
  filter(speaker_id %in% nchild) %>%
  group_by(speaker_id)
}

child_month_dev <- mtld_filter(child_month_mtld)

# combine mom and child data
combine_month_dev <- child_month_dev %>%
  filter(speaker_id %in% mom_id) %>%
  group_by(speaker_id) %>%
  rename(mtld.x = mtld,
         length.x = length) %>%
  left_join(select(mom_month_mtld, -target_child_id)) %>%
  rename(mtld.y = mtld,
         length.y = length) %>%
  group_by(corpus_id, speaker_id) %>%
  arrange(corpus_id, speaker_id, age) 

test_model <- lm(mtld.y ~ log(age),combine_month_dev)
plot(test_model) #check redisual plot

# data transformation 
combine_month_trans <- combine_month_dev %>%
  mutate(mtld.y = log2(mtld.y),
         mtld.x = sqrt(mtld.x),
         lag.x = lag(mtld.x),
         lag.y = lag(mtld.y),
         lag.x2 = lag(mtld.x, n=2),
         lag.y2 = lag(mtld.y, n=2),
         lag.x3 = lag(mtld.x,n=3),  
         lag.y3 = lag(mtld.y, n= 3),
         lag.x4 = lag(mtld.x,n=4),  
         lag.y4 = lag(mtld.y,n=4),
         lag.x5 = lag(mtld.x,n=5),
         lag.y5 = lag(mtld.y, n=5))



# 
lm_lg <- lm(scale(mtld.x) ~ log(age) + scale(lag.x) + scale(mtld.y), data = combine_month_trans)
summary(lm_lg)

lm_mom_lag <- lm(mtld.x ~ lag.y5 + (1+lag.y5) * factor(speaker_id), data = combine_month_dev)
summary(lm_mom_lag)



# get moms' growth slope

lm_mom <- lm(mtld.y ~  (1+lag.y5) * factor(speaker_id), combine_month_dev5)
summary(lm_mom)

mom_slope <- data_frame(slope = lm_mom$coefficients) 
row <- c(2,29:54) 

mom_slope <- subset(mom_slope, rownames(mom_slope) %in% row)
baseline = as.numeric(mom_slope[1,])
mom_slope[c(2:27),] = mom_slope[c(2:27),] + baseline 
mom_slope$speaker_id <- child_num

            
              
lmer_dev <-
  lmer(scale(mtld.x) ~ scale(lag.x) * log(age) + scale(lag.y5)  + (1 | speaker_id), combine_month_dev)
summary(lmer_dev)


```



