---
title             : "Lexical Diversity and Vocabulary Development"
shorttitle        : "Lexical Diversity"

author: 
  - name          : "Yawen Yu"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "shellyyu@uchicago.edu"
  - name          : "Daniel Yurovsky"
    affiliation   : "2"


affiliation:
  - id            : "1"
    institution   : "University of California, Los Angeles"
  - id            : "2"
    institution   : "University of Chicago"

author_note: |

  Please address corresponsdence

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.
  
keywords          : "cognitive development; language acquisition; corpus analysis"
wordcount         : "X"

bibliography      : ["lexdiv.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library(papaja)
library(tidyverse)

```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used  for all our analyses.


# Results

# Discussion

# Acknowledgements

We are grateful to the members of the Communication and Learning Lab for feedback on this project and manuscripti. This work was supported by a James S. McDonnell Foundation Scholar Award to DY. 


\newpage

# References


```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\noindent
